A Phenomenological Model for the Intra-Cluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-04-17 paper1.tex
small change

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. Their sample contains clusters up to $z \approx
0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
our mass cut) which however is not used throughout the rest of the work. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.1$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.

>>>>

In the right panel of Fig.~\ref{fig:X_LM}, we compare the
$Y_{\rmn{SZ}}-M_{500}$ relation in our model (calculated as in equation~(3) of
\citealp{2011arXiv1109.3709B}) with the observed scaling relation by the
\cite{2013arXiv1303.5080P}. {\bf We compare with the result obtained from the \emph{Planck} Cosmo 
sample with Malmquist bias correction (see their Table~A.1).} Their sample contains clusters 
up to $z \approx 0.45$ and has a median of $z \approx 0.15$; hence, we compare the data to our
relation at the MultiDark snapshot $z=0.16$ (that contains 11419 clusters above
our mass cut) which however is not used throughout the rest of the work. Our
model reproduces the data remarkably well, except for the high-mass end where
our simulations have a weaker constraining power due to the smaller box size in
comparison to the survey volume of {\em Planck}.  We find a scatter of
$\sigma_{yx} \approx 0.11$ which compares well with the \emph{Planck} result of
$\sigma_{yx} \approx 0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling
relations for different redshifts.
